---
title: "Assignment 1"
---

# Assignment 1

My first assignment has three parts.

## (a) 

I want to write about this video that I watched on YouTube: [The R Language The Good The Bad & The Ugly • John Cook • GOTO 2012](https://www.youtube.com/watch?v=6S9r_YbqHy8).

In a brief summary of the video, I can say that it's primarily an in-depth and explanatory conference presentation about R. At the beginning of the conference, a particular example caught my attention, where the speaker emphasized, 'You don't have a soul, doctor, you have a soul.' Taking inspiration from this analogy, the speaker concluded that R is not just a language; R has a language. The conferance proceeded to discuss how R is a highly useful tool in data analytics, supported by various examples. Another part of the presentation that I found appealing was an example from Francois Pinard: 'Using R is a bit akin to smoking. The beginning is difficult; one may get headaches few times. But in the long run, it becomes pleasurable and even addictive.' Additionally, the speaker compared R with other programming languages, highlighting the differences. In the end, I can say it was a useful and attention-grabbing conference presentation.

## (b) 

There are some fundamental differences between the R and Python programming languages.

**1)** R uses 1 based indexing, while Python uses 0 based indexing. It means that in R, first element of a vector is starting with index 1; in Python, it starts with index 0.

```{r}
school_days <- c("Monday","Tuesday","Wednesday","Thursday","Data Analytics")
first_index <- school_days[1]
first_index
```

```{python}
work_days = ["Monday","Tuesday","Wednesday","Thursday","Data Analytics"]
first_index_ = work_days[0]
print(first_index_)
```

## (c) 

```{r}
library(dslabs)
data("na_example")
na_example
sum(is.na(na_example))
delete_na <- ifelse(is.na(na_example), 0, na_example)
delete_na
sum(is.na(delete_na))
```
